DS Tuc b is Aligned?

### 2019-08-30 paper/main.tex
minor edits

\begin{document}
\title{DS Tuc b is Aligned}

@@

@@

@@

It's aligned!

@@

\software{%
    numpy \citep{numpy},
    matplotlib \citep{matplotlib},
    scipy \citep{jones01}
    tensorflow \citep{tensorflow},
    lightkurve\footnote{https://doi.org/10.5281/zenodo.2557026},
    photutils\footnote{https://doi.org/10.5281/zenodo.2533376},
    astropy\citep{astropy:2013, astropy18},
    eleanor\citep{Feinstein19},
    \btmtodo{Fix}
    }

\facility{TESS, \btmtodo{Magellan}}

>>>>

\begin{document}
\title{DS Tuc b is Aligned?}

@@

\author{Began Medell}

@@

We model the inferred radial velocities with version 1.0.0.dev3 of the \textit{starry} package of \citet{Luger19}.

@@

It's aligned?

@@

\software{%
    numpy \citep{numpy},
    matplotlib \citep{matplotlib},
    scipy \citep{Jones01}
    astropy \citep{Astropy18},
    eleanor \citep{Feinstein19},
    starry \citep{Luger19},
    exoplanet \citep{Foreman-Mackey19},
    theano
    }

\facility{TESS, Magellan:Clay (Planet Finder Spectrograph)}
